Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

The part of the paper from this point onwards until the appendix will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{app:kSJ}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.

>>>>

The part of the paper from this point onwards until the appendix will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{app:ksj}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.
